Trends of downward SDR in Thessaloniki

### 2023-05-07 Article.Rmd
Commit 2023-05-06 11:17
Commit 2023-05-07 14:17

<!-- time span -->
The global radiation was obtained from the pyranometer CM-21, for the period
`r min(ALL_1_daily_DESEAS$Date)` -  `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we used direct radiation data for comparisons, obtained by a CM-21 pyrheliometer, with data span
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` - `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

@@

@@

## Long-term trends

>>>>

......

<!-- time span -->
The global radiation was obtained from the pyranometer CM-21, for the period from
`r min(ALL_1_daily_DESEAS$Date)` to `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we auxialiary used direct radiation data for comparisons, obtained by a CM-21 pyrheliometer, with data span from 
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

......

@@

......

@@
